\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-10 paper/paper.tex
Fixed some things in paper

The graph isomorphism problem is the computational problem of determining whether two finite graphs are isomorphic. Besides its practical importance, the graph isomorphism problem is a curiosity in computational complexity theory as it is one of a very small number of problems belonging to NP neither known to be solvable in polynomial time nor NP-complete: it is one of only 12 such problems listed by Garey \& Johnson (1979)\cite{book:garyJohnson1979}, and one of only two on that list whose complexity remains unresolved. As of 2008 the best algorithm (Eugene Luks, 1983) has run time $2^{O(\sqrt{n log n})}$ for graphs with \emph{n} vertices.\cite{article:davidJohnson2005}\cite{inproceedings:babaiCodenotti2008}\cite{website:wikiGI}

@@

The results of the experiment are shown in table \ref{table:results}. Seven sets of graphs were tested for isomorphisms and in three cases the computation time was significantly different. In the other cases, the preprocessing time is relatively very small. This is because the low complexity of \emph{gettwins} and the fact that \emph{preprocessing} does nothing when there are no (false) twins. The difference in computation time is not related to the preprocessing time, as the preprocessing time is not equal to the difference in computation times. This is likely due to the circumstances of both executions of the algorithms not occurring under the exact same circumstances, as it was impossible to ensure the conditions were the same.

>>>>

The graph isomorphism problem is the computational problem of determining whether two finite graphs are isomorphic. Besides its practical importance, the graph isomorphism problem is a curiosity in computational complexity theory as it is one of the few problems belonging to NP neither known to be solvable in polynomial time nor NP-complete: it is one of only 12 such problems listed by Garey \& Johnson (1979)\cite{book:garyJohnson1979}, and one of only two on that list whose complexity remains unresolved. As of 2008 the best algorithm (Eugene Luks, 1983) has run time $2^{O(\sqrt{n log n})}$ for graphs with \emph{n} vertices.\cite{article:davidJohnson2005}\cite{inproceedings:babaiCodenotti2008}\cite{website:wikiGI}

@@

The results of the experiment are shown in table \ref{table:results}. Seven sets of graphs were tested for isomorphisms and in three cases the computation time was significantly shorter. In the other cases, the preprocessing time is relatively short compared to the total computing time. This is because the low complexity of \emph{gettwins} and the fact that \emph{preprocessing} does nothing when there are no (false) twins. The difference in computation time is not related to the preprocessing time, as the preprocessing time is not equal to the difference in computation times. This is likely due to the circumstances of both executions of the algorithms not occurring under the exact same circumstances, as it was impossible to ensure the conditions were the same.
